---
title: "R Markdown Example"
author: "Ariel Chernofsky"
date: "2/17/2022"
output:
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = " ")
```


An alternative option (or in addition) to having separate code files for each part of the analysis, a single well documented RMarkdown file can be used. 

When using RMarkdown with GitHub, if we add the option to the YAML header `keep_md: true`, then we can view the rendered document on GitHub.

```{r libraries}

library(dplyr)
library(ggplot2)
library(broom)

```

# Data manipulation

I like using the **dplyr** package from the [tidyverse](https://www.tidyverse.org/) ecosystem. 

```{r}

data("iris")

iris_sub <- iris %>%
  rename_all(tolower) %>%
  dplyr::filter(species != "setosa", sepal.length > 2)


```

# Summary statistics

**dplyr** also has some great functions for calculating summary statistics.

```{r}

iris_sub %>%
  group_by(species) %>%
  summarize(N = n(),
            mean_slen = mean(sepal.length),
            median_slen = median(sepal.length),
            sd_slen = sd(sepal.length))

```

# Exploratory plots

**ggplot2** is another package that is part of the [tidyverse](https://www.tidyverse.org/) ecosystem that can generate nice plots.

```{r}

ggplot(aes(sepal.width, petal.length, color = species), data = iris_sub) + 
  geom_point() + 
  theme_minimal()

```

# Fit a linear model

We can regress petal length against sepal width and length to estimate the relationship between these variables.

```{r}
lm1 <- lm(petal.length ~ sepal.width + sepal.length, data = iris_sub)
```

The **broom*** package has functions such as `tidy` and `glance` that nicely organize the output from many commonly used R packages.

```{r}
tidy(lm1)
glance(lm1)
```

